C_exp_1

### 2018-08-11 experiments/C_exp_1/writeup/C_exp_1.Rmd
restructure or standardise C

```{r 'load Libraries and source my functions', message=FALSE, echo=FALSE}
library(knitr)
library(tidyverse)
library(tidymodels)
library(broom.mixed)
library(lme4)
library(lmerTest)
library(dotwhisker)
library(kableExtra)
library(LMERConvenienceFunctions)
library(data.table)
library(gridExtra)
source('summarySEwithin2.R')
source('concatenate_raw_data.R')
source('add_borderline_vars.R')
source('annotate_the_raw_data.R')
source('declare_impossible_rt.R')
source('remove_impossible_trials.R')
source('pretty_coef_table.R')
source('pretty_coef_plot.R')
```

```{r, "get data for RT analysis", echo=F, message=F, warning=F, results='hide'}
dat <- 
  concatenate_raw_data() %>%
  annotate_the_raw_data() %>% # at this point RT has min=1 (resp_type="sticky") and max=59,999 (resp_type="timeout")
  filter(RT>1 & RT<59999) # at this point RT has min=445, max=42,685 (42 seconds) and nrow(dat) is 7677 down from 7680
dat <- perSubjectTrim.fnc(dat, response='RT', subject='Subject', trim = 2.5)$data %>% select(-SD, -Mean, -Scaled)
dat$RT_log <- log(dat$RT)
```

```{r, "get data for borderline analysis", echo=F}
dat_borderline <- 
  concatenate_raw_data() %>%
  add_borderline_vars() %>%
  annotate_the_raw_data() %>% # at this point RT has min=1 (resp_type="sticky") and max=59,999 (resp_type="timeout")
  filter(RT>1 & RT<59999) # at this point RT has min=445, max=42,685 (42 seconds) and nrow(dat) is 7677 down from 7680
```

@@

```{r, echo=FALSE}
instructions_table <- 
  dat %>%
    select(Item, Quantity, Vagueness, Number, Instruction) %>%
    unique() %>%
    arrange(Item, Quantity, Vagueness, Number) %>%
    spread(key=Vagueness, value=Instruction)
```

```{r, echo=FALSE}
instructions_table %>% 
  kable(align='cccll', caption="Full table of instructions") %>% 
      kable_styling(full_width = F, position = "left", font_size = 11) 
```

```{r, echo=FALSE, eval=FALSE}
kable(instructions_table, format="latex", booktabs = TRUE)
```

>>>>

```{r 'load Libraries and source my functions', message=FALSE, echo=FALSE}
library(knitr)
library(tidyverse)
library(broom)
library(broom.mixed)
library(lme4)
library(lmerTest)
library(dotwhisker)
library(kableExtra)
library(LMERConvenienceFunctions)
library(data.table)
library(gridExtra)
source("C_exp_1_functions/concatenate_raw_data.R")
source("C_exp_1_functions/annotate_the_raw_data.R")
source("C_exp_1_functions/add_borderline_vars.R")
source("C_exp_1_functions/pretty_coef_table.R")
source("C_exp_1_functions/summarySEwithin2.R")
root_dir <- getwd()
data_dir <- "C_exp_1_data"
```

```{r, "get data for RT analysis", echo=F, message=F, warning=F, results='hide'}
dat <- 
  concatenate_raw_data(root_dir, data_dir) %>%
  annotate_the_raw_data() %>% # at this point RT has min=1 (resp_type="sticky") and max=59,999 (resp_type="timeout")
  filter(RT>1 & RT<59999) # at this point RT has min=445, max=42,685 (42 seconds) and nrow(dat) is 7677 down from 7680
dat <- perSubjectTrim.fnc(dat, response='RT', subject='Subject', trim = 2.5)$data %>% select(-SD, -Mean, -Scaled)
dat$RT_log <- log(dat$RT)
```

```{r, "get data for borderline analysis", echo=F}
dat_borderline <- 
  concatenate_raw_data(root_dir, data_dir) %>%
  add_borderline_vars() %>%
  annotate_the_raw_data() %>% # at this point RT has min=1 (resp_type="sticky") and max=59,999 (resp_type="timeout")
  filter(RT>1 & RT<59999) # at this point RT has min=445, max=42,685 (42 seconds) and nrow(dat) is 7677 down from 7680
```

@@

```{r, echo=FALSE}
instructions_table <- 
  dat %>%
    select(Item, Quantity, Vagueness, Number, Instruction) %>%
    unique() %>%
    arrange(Item, Quantity, Vagueness, Number) %>%
    spread(key=Vagueness, value=Instruction)
# kable(instructions_table, format="latex", booktabs = TRUE)
instructions_table %>% 
  kable(align='cccll', caption="Full table of instructions") %>% 
      kable_styling(full_width = F, position = "left", font_size = 11) 
```
